A Data-Driven Framework for Neural Field Modelling

### 2010-11-16 ltx/first_order_framework/LaTeX_Manuscript.tex
up to discussion for Davids edits

% The size of the squares in the figure show the magnitude of the log of the error. The squares are black if the log of the error is negative (the RMSE is $<1$) and the squares are white if the log of the error is positive (the RMSE is $>1$). The largest black squares indicate the best performance and the largest white squares indicate the worst performance for the parameter combinations (\dean{need some thing more quantitative}). 
From Figure~\ref{fig:Figure12} it can be seen that the estimation accuracy depends the parameters of the sigmoid function. \dean{This next bit is CRAP (help):} When the threshold is negative or the slope is very gentle, all of the activity is being passed through the sigmoid function. However, as the slope is increased or the threshold is increased, more of the field is within the saturating region of the activation function. This is illustrated in Figure~\ref{fig:sigmoidfunctions}, where the sigmoids from the bottom left corner through to near top right corner of Figure~\ref{fig:sigmoidfunctions} are plotted. This appears to have a detrimental effect on the estimation accuracy.

\subsubsection{Experiment IV: Results for Varying the Sensor Kernel Width}
The accuracy of the estimation algorithm was tested for observation kernels by varying the width parameter. Figure~\ref{fig:Figure12} shows the RMSE of the connectivity kernel estimates for the various connectivity kernel widths. The figure shows that there is error a desirable connectivity kernel width range. As the the theory presented earlier in Section~\ref{SpectralAnalysisSection} suggests, the observation kernel acts as a spatial filter. When the observation kernel is to narrow, a small amount of aliasing appears to be increasing the estimation error. When the observation kernel width is initially increased the error drops. As expected when the observation kernel becomes too large, important spatial frequency information is lost and the error becomes larger.

@@

\subsection{Implications for Experiment Design}
As seen in Figures~\ref{fig:Figure7} and~\ref{fig:Figure10}, the results indicate accurate estimation for the connectivity kernel parameters, where the mean parameter estimates are in good agreement with the actual values and the true kernel lies within the 95~\% confidence intervals of the estimates. The estimates of the connectivity kernel parameters show relatively broad distributions, which can be expected considering the system's input is modelled as a random disturbance, and the observations are corrupted by noise. To overcome the effect of noise, the use of a controlled input stimulus should be considered when applying the estimation algorithm to electrophysiological recordings. Given knowledge of the input and the appropriate model, it is expected that the variance of the parameter estimates will decrease. Even when using an input, our results imply that we should only expect to learn distributions of parameters, rather than uncover a `true' parameter set. By designing an input signal carefully and using an evoked-potential paradigm, where stimuli are repeated many times, data could be epoched into (and averaged over) a sufficient number of trials (realisations), where each trial is a response to a stimulus, such that a distribution of the parameter estimates can be formed.

>>>>

% The size of the squares in the figure show the magnitude of the log of the error. The squares are black if the log of the error is negative (the RMSE is $<1$) and the squares are white if the log of the error is positive (the RMSE is $>1$). The largest black squares indicate the best performance and the largest white squares indicate the worst performance for the parameter combinations (\dean{need some thing more quantitative}). 
From Figure~\ref{fig:Figure12} it can be seen that the estimation accuracy depends the parameters of the sigmoid function. \dean{This next bit is CRAP (please help):} When the threshold is negative or the slope is very gentle, all of the activity is being passed through the sigmoid function. However, as the slope is increased or the threshold is increased, more of the field is within the saturating region of the activation function. This is illustrated in Figure~\ref{fig:sigmoidfunctions}, where the sigmoids from the bottom left corner through to near top right corner of Figure~\ref{fig:sigmoidfunctions} are plotted. This appears to have a detrimental effect on the estimation accuracy.

\subsubsection{Experiment IV: Results for Varying the Sensor Kernel Width}
The accuracy of the estimation algorithm was tested for different observation kernels by varying the width parameter, $\sigma_m$. Figure~\ref{fig:Figure13} shows the RMSE of the connectivity kernel estimates for the various observation kernel widths. As the theory presented earlier in Section~\ref{SpectralAnalysisSection} suggests, the observation kernel acts as a spatial filter and when the observation kernel is to narrow, high spatial frequency information is present but not adequately sampled by the observation function. Therefore, a small amount of aliasing occurs which results in the estimation error. When the observation kernel width is increased, the high spatial frequency information is filtered by the observation kernel and the error decreases. However, as expected, when the observation kernel becomes too large, important spatial frequency information is lost and the error becomes larger.

@@

\subsection{Implications for Experimental Design}
As seen in Figures~\ref{fig:Figure7} and~\ref{fig:Figure10}, the results indicate accurate estimation for the connectivity kernel parameters, where the mean parameter estimates are in good agreement with the actual values and the true kernel lies within the 95~\% confidence intervals of the estimates. The estimates of the connectivity kernel parameters show relatively broad distributions, which can be expected considering the system's input is modelled as a random disturbance, and the observations are corrupted by noise. To overcome the effect of noise, the use of a controlled input stimulus should be considered when applying the estimation algorithm to electrophysiological recordings. Given knowledge of the input and the appropriate model, it is expected that the variance of the parameter estimates will decrease. Even when using an input, our results imply that we should only expect to learn distributions of parameters, rather than uncover a `true' parameter set. By designing an input signal carefully and using an evoked-potential paradigm, where stimuli are repeated many times, data could be epoched into (and averaged over) a sufficient number of trials (realisations), where each trial is a response to a stimulus, such that a distribution of the parameter estimates can be formed.
